Supplementary Material to ``External Prior Guided Internal Prior Learning for Real Noisy Image Denoising"

### 2016-11-15 1047_sp.tex
ad

>>>>

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 35.21dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 35.25dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 35.21dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
{\footnotesize (d) MLP \cite{mlp}: 37.18dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
{\footnotesize (e) CSF \cite{csf}: 38.10dB }
\end{minipage}
}\vspace{-3mm}
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 38.62dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
{\footnotesize (g) NI \cite{neatimage}: 37.41dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 39.53dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
{\footnotesize (i) Ours: \textbf{39.87}dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 1600 B2" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig14}
\end{figure}
